The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth

### 2022-01-25 paper/paper.Rmd
Edited several sentences.

<!--The next paragraph, which begins “The anomalies are also found” should perhaps be “Similar anomalies were found.” Was it the same respondents with the extremely high wages that showed extremely high number of hours of work? I suspect not, but please be explicit.-->
<!--AE comment: Rewrite this sentence. "Observations" aren't working 420 hours. A "respondent" might have been reported as having worked 420 hours per week.--> The anomalies are also found in the total hours of work, where some observations reported as having worked for 420 hours a week in total. 
According to @MichaelRPergamit2001DWTN, one of the flaws of the NLSY79 employment data is that the NLSY79 collects the information of the working hours since the last interview. Thus, it might be challenging for the respondents to track the within-job hours' changes between survey years, especially for the respondents with fluctuating working hours or seasonal jobs. It even has been more challenging since 1994, where the respondents had to recall two year periods. This shortcoming might also contribute to the fluctuation of one's wages data.

@@

<!--AE comment: Section 3.2.1 begins “As part of the IDA, which is the model formulation, we build a robust linear regression model to treat the extreme values in the data.” This could use clarification. In 3.2, you said that part of IDA is “ model formulation without any formal statistical inference.” To me, that sounds like using modeling as a descriptive technique, and it’s something I would consider to be more a part of EDA. But then in 3.2.1, while it is perhaps not using modeling in an inferential way, the model is being used for more than just description. I might rephrase the first sentence as follows: “In order to treat the extreme values in the data, we built a robust linear regression model.” -->
As part of the IDA, <!--AE comment: Awkward sentence. "which is the model formulation"?--> which is the model formulation, we build a robust linear regression model to treat the extreme values in the data. Robust linear regression yields an estimation robust to the influence of noise or contamination [@KollerManuel2016rARP]. It also aims to detect the contamination by weighting each observation based on how "well-behaved" they are, known as robustness weight. Observations with lower robustness weight are suggested as an outlier by this method [@KollerManuel2016rARP].

>>>>

<!--The next paragraph, which begins “The anomalies are also found” should perhaps be “Similar anomalies were found.” Was it the same respondents with the extremely high wages that showed extremely high number of hours of work? I suspect not, but please be explicit.-->
<!--AE comment: Rewrite this sentence. "Observations" aren't working 420 hours. A "respondent" might have been reported as having worked 420 hours per week.--> The anomalies are also found in the total hours of work, where some observations reported as having worked for 420 hours a week in total. 
According to @MichaelRPergamit2001DWTN, one of the flaws of the NLSY79 employment data is that the NLSY79 collects the information of the working hours since the last interview. Thus, it might be challenging for the respondents to track the within-job hours' changes between survey years, especially for the respondents with fluctuating working hours or seasonal jobs. It even has been more challenging since 1994, after which respondents were only surveyed every other year and thus had to recall two full years’ job history. This shortcoming might also contribute to the fluctuation of one's wages data.

@@

<!--AE comment: Section 3.2.1 begins “As part of the IDA, which is the model formulation, we build a robust linear regression model to treat the extreme values in the data.” This could use clarification. In 3.2, you said that part of IDA is “ model formulation without any formal statistical inference.” To me, that sounds like using modeling as a descriptive technique, and it’s something I would consider to be more a part of EDA. But then in 3.2.1, while it is perhaps not using modeling in an inferential way, the model is being used for more than just description. I might rephrase the first sentence as follows: “In order to treat the extreme values in the data, we built a robust linear regression model.” -->
As part of the IDA, <!--AE comment: Awkward sentence. "which is the model formulation"?--> which is the model formulation, we build a robust linear regression model to treat the extreme values in the data. Robust linear regression yields an estimation robust to the influence of noise or contamination [@KollerManuel2016rARP]. It also aims to detect the contamination by weighting each observation based on how "well-behaved" they are, known as robustness weight. An observation with a lower robustness weight would be suggested as an outlier [@KollerManuel2016rARP].
